\begin{abstract}
Hybrid offline-to-online reinforcement learning for transit control is attractive because operators often have rich historical data but only imperfect simulators.
However, a bus holding policy tuned in one city may fail in another city unless the target simulator is manually calibrated, and such calibration is expensive.
We study this cross-city transfer problem for bus holding using four open transit city bundles: Singapore, Austin/CapMetro, Halifax Transit, and MBTA.
We propose Causal-Factored Cross-City Model Transfer (\ours), a mechanism-wise residual world-model adapter that decomposes dense simulator corrections into headway, demand/dwell, speed, and reward mechanisms, and optionally reweights source cities by static speed, headway, route, and demand similarity.
Against a dense \Htwo-style residual baseline, \ours is evaluated under a strict leave-one-city-out protocol in which each of the four cities is the target exactly once.
On static-derived cross-city dynamics validation, unweighted \ours beats \Htwo on all four targets with mean total-MSE ratio $0.759$, while similarity-weighted \ours also wins on all four targets and lowers the mean ratio to $0.578$.
In one-step policy validation, \ours improves reward/regret on three of four targets and lowers bunching rate on all four targets.
Calibration-budget, per-mechanism, ablation, route-bootstrap, source-subset, and generator-bias checks support the same main trend while showing that the advantage depends on multi-source diversity and should not be overstated as superiority on every small city subset.
On two public Austin raw APC/AVL slices, source-only \ours is more stable than dense residual transfer but still worse than a state-informed passive no-correction baseline; with few-shot target residual calibration, a residual gate beats that passive baseline at $1\%$ target line-group budget in both slices.
The resulting contribution is a reproducible, reviewer-facing protocol and an empirically supported boundary condition: mechanism-factored transfer is useful for low-calibration cross-city residual adaptation, but counterfactual control or field validation remains necessary before operational claims.
\end{abstract}
