\section{Introduction}

Bus holding control aims to reduce headway instability by delaying selected vehicles at stops.
The control problem is local in execution but system-wide in consequence: a hold action changes forward and backward headways, passenger waiting, dwell, and downstream bunching.
Modern reinforcement learning (RL) methods can learn holding policies in simulation, but practical deployment is constrained by two persistent gaps.
First, high-fidelity simulation and manual calibration are expensive to reproduce in each city.
Second, public data availability differs sharply across agencies: one city may expose speed bands and passenger OD data, while another may only provide GTFS schedules and coarse ridership summaries.

Hybrid offline-to-online methods such as \Htwo learn from both logged data and simulator interaction by correcting or reweighting dynamics gaps \citep{niu2022h2o,liu2024h2oplus}.
This is a natural starting point for transit systems, where a historical buffer and a lower-fidelity simulator are often available.
The difficulty is cross-city transfer.
A dense monolithic residual model can fit simulator error in the source cities, but its parameters mix mechanisms that may shift differently across cities: schedule headways, route speeds, stop demand, and dwell behavior do not all change together.
If cross-city transfer depends on localized changes in mechanisms, a factored representation should be more stable than a dense one \citep{bengio2020meta,feng2022factored}.

This paper studies that hypothesis in a deliberately conservative setting.
We do not claim that the current data are vehicle-level real-world trajectories.
Instead, we construct full-route open transit city bundles and evaluate models on static-data-derived offline dynamics targets.
The protocol is meant to answer a narrower question: when only open static data and an uncalibrated simulator-like transition generator are available, does a mechanism-factored residual adapter transfer better across cities than a dense \Htwo-style residual correction?

We introduce Causal-Factored Cross-City Model Transfer (\ours).
\ours fits residual corrections at the level of output mechanisms rather than one dense residual over all outputs.
For each target quantity, it uses a mechanism-specific sparse parent set: headway and gap outputs depend primarily on neighboring headways, target headway, speed, time, and action; demand and dwell outputs depend on waiting passengers, speed, target headway, time, and action; speed outputs use speed, time, and route-position features; reward uses policy-relevant headway and waiting quantities.
We also add a city-similarity source weighting rule that uses only static descriptors available before target calibration.

The paper contributes:
\begin{enumerate}[leftmargin=1.5em]
    \item A cross-city open-transit validation protocol using four full-route city bundles and a strict leave-one-city-out evaluation unit.
    \item A mechanism-wise residual transfer model and a static descriptor based source weighting rule.
    \item A set of reviewer-facing diagnostics: source-weight sensitivity, source-subset robustness, generator-bias/noise robustness, and traffic-domain policy metrics.
    \item An explicit boundary on the claim: the evidence supports static-derived cross-city transfer and not yet operational deployment without vehicle-level validation.
\end{enumerate}
