\section{Problem Setting}

Let $s_t \in \Sstate$ denote a bus-system state at a decision event and $a_t \in \Aact$ denote a holding action in seconds.
The state contains line and station identifiers, time of day, direction, forward and backward headways, waiting passengers, target headway, base dwell, co-line headways, gap, and segment speed.
The transition target is
\[
    \y_t =
    (h^+_{t+1}, h^-_{t+1}, q_{t+1}, d_{t+1}, g_{t+1},
     \bar h^+_{t+1}, \bar h^-_{t+1}, v_{t+1}, r_{t+1}),
\]
covering next headways, waiting passengers, dwell, gap, co-line headways, speed, and reward.

Each city $c$ provides a bundle $\D_c$ of route, timetable, speed, and demand tables.
From these tables we construct paired simulator and static-derived target transitions:
\[
    \y^{\mathrm{sim}} = f_0(s,a), \qquad
    \y^{\mathrm{target}} = f_c(s,a),
\]
and train residual models on
\[
    \Delta_c(s,a) = \y^{\mathrm{target}} - \y^{\mathrm{sim}}.
\]
For cross-city validation, source cities $\mathcal{C}_{\mathrm{src}}$ are used for fitting and a held-out target city $c^\star$ is used only for evaluation.

The main evaluation unit is a city target, not a route.
For four cities, the strict leave-one-city-out protocol has exactly four target evaluations:
\[
    \{(\mathcal{C}\setminus\{c\}) \rightarrow c : c \in \mathcal{C}\}.
\]
This avoids counting repeated target cities as independent evidence.

\paragraph{Claim scope.}
The target transitions are static-data-derived pseudo-observations.
They combine agency data, schedule-derived speeds or headways, passenger-demand summaries, and deterministic transition rules.
They are useful for reproducible cross-city validation, but they are not vehicle-level AVL/APC ground truth.
Accordingly, the paper evaluates transfer robustness under open static-data-derived dynamics, not operational field performance.
