\section{Method}

\subsection{Dense \Htwo-style residual baseline}

The \Htwo-style baseline fits one dense residual model over all transition outputs:
\[
    \hat \Delta_{\mathrm{dense}}(s,a) = \phi_{\mathrm{dense}}(s,a)^\top B,
\]
where $\phi_{\mathrm{dense}}$ includes normalized state/action features, squares, action interactions, and selected pairwise products.
At evaluation time the corrected prediction is
\[
    \hat \y_{\Htwomath}(s,a) = f_0(s,a) + \hat \Delta_{\mathrm{dense}}(s,a).
\]
The baseline is intentionally strong: it can use many cross terms and is fit on all source-city transitions.

\subsection{Causal-factored residual transfer}

\ours decomposes the residual by output mechanism:
\[
    \hat \Delta_j(s,a) = \phi_j(s,a)^\top \beta_j, \qquad j \in \{1,\ldots,9\}.
\]
The feature map $\phi_j$ is chosen according to the output mechanism.
Headway and gap residuals use current headways, target headway, speed, action, and time.
Waiting and dwell residuals use waiting passengers, target headway, speed, station fraction, action, and time.
Speed residuals use current speed, event time, and station position.
Reward residuals use policy-relevant headway deviations, waiting passengers, gap, speed, action, and time.
The corrected prediction is
\[
    \hat \y_{\oursmath}(s,a)
    = f_0(s,a) +
      \left(\hat\Delta_1(s,a),\ldots,\hat\Delta_9(s,a)\right).
\]
All reported models use ridge-regularized sufficient statistics, so the experiment can be reproduced without stochastic neural training.

\subsection{Source-city similarity weighting}

For each city we compute a static descriptor $z_c$ from speed quantiles, headway quantiles, route-distance quantiles, peak-demand hour, and the 24-hour demand-share vector.
For a target city $t$ and source city $c$, the distance is computed after feature-wise standardization over the source-plus-target set:
\[
    d(c,t) =
    \frac{1}{\sqrt{m}}\left\|
    \frac{z_c-\mu}{\sigma} -
    \frac{z_t-\mu}{\sigma}
    \right\|_2.
\]
The source weight is
\[
    w_c =
    \frac{\exp(-d(c,t)/T) + \lambda \max_{c'} \exp(-d(c',t)/T)}
         {\sum_{k \in \mathcal{C}_{\mathrm{src}}}
          \left[\exp(-d(k,t)/T) + \lambda \max_{c'} \exp(-d(c',t)/T)\right]}.
\]
The default values are $T=1.0$ and $\lambda=0.05$.
The source sufficient statistics are rescaled so that these weights control the effective number of source transitions rather than simply reflecting raw city size.

\subsection{One-step policy validation}

For policy-level validation, each method evaluates a discrete hold set
$\{0,15,30,45,60\}$ seconds under a set of headway-stress states.
The policy selects the action with the highest predicted reward under its corrected transition model.
The selected action is then scored against the static-derived target transition.
We report reward, regret to an oracle action, mean absolute headway error, bunching rate, large-gap rate, and mean hold seconds.
This is a policy-level one-step lookahead benchmark, not a live SUMO rollout.
