\section{Experiments}

\subsection{Data}

We evaluate on four full-route city bundles.
Singapore uses LTA DataMall passenger-volume and OD bus data with traffic speed bands.
Austin/CapMetro uses GTFS schedules with demand proxied from scheduled headways.
Halifax Transit uses route-level APC summaries apportioned over GTFS route-direction patterns.
MBTA uses Fall 2025 stop-level boardings and alightings apportioned over GTFS route-direction patterns.
\Cref{tab:dataset} summarizes the bundles and their evidence levels.

\begin{table}[t]
\centering
\scriptsize
\resizebox{\textwidth}{!}{\input{../cf_h2o/results/paper_artifacts/tables/dataset_table.tex}}
\caption{Open transit city bundles. Evidence levels distinguish observed passenger/traffic data from schedule-derived proxies.}
\label{tab:dataset}
\end{table}

\subsection{Validation protocols}

\paragraph{Primary dynamics validation.}
The main dynamics experiment is strict leave-one-city-out.
Each city is held out once as the target, and all remaining cities are used as sources.
The metric is total MSE averaged over the nine transition outputs.
Ratios below 1 indicate improvement over the dense \Htwo-style residual baseline.

\paragraph{Policy validation.}
The one-step policy experiment uses the same source-target splits and evaluates action selection under headway-stress states.
We report reward/regret and traffic-domain metrics.
Bunching rate is the fraction of decisions in which either adjacent headway is below $0.5$ times the target headway.
Large-gap rate is the fraction in which either adjacent headway exceeds $1.5$ times the target headway.

\paragraph{Reviewer-facing robustness checks.}
We include diagnostics targeted at common review objections.
First, a target-construction audit separates observed, apportioned, schedule-proxy, and deterministic target components.
Second, a target-route calibration-budget sweep adds $0\%$, $1\%$, $5\%$, $10\%$, $25\%$, or $100\%$ of held-out target-city routes to the source sufficient statistics and evaluates on the remaining target routes; the $100\%$ point is an in-sample oracle reference.
Third, per-mechanism errors decompose total MSE into headway/gap, demand/dwell/reward, and speed groups.
Fourth, mechanism ablations compare the proposed parent sets against wrong mechanism groupings, action/time-only features, and dense matched-capacity variants.
Fifth, source-weight sensitivity varies $T \in \{0.5,1.0,2.0\}$ and $\lambda \in \{0,0.05,0.1\}$, while source-subset and pairwise-source checks remove major source families.
Sixth, generator robustness perturbs output groups or adds measurement-noise terms to the evaluation sufficient statistics.

\paragraph{External real APC/AVL validation.}
To partially address the static-derived target limitation, we add an external Austin/CapMetro validation slice from public raw APC stop-event data.
The July--December 2021 and August 2016 files contain observed stop events with boardings, alightings, vehicle load, dwell time, vehicle position, route, trip, stop, and vehicle identifiers.
We filter records with valid stop, trip, GPS, and import-quality flags, reconstruct stop-level headways by route-direction-stop event times, and evaluate passive action-$0$ one-step dynamics against the observed next stop event.
The no-correction baseline in this experiment is a state-informed passive transition using the APC-derived current state, not a schedule-only free-running simulator.
This is real historical APC/AVL validation, but it is still offline passive validation rather than a field control deployment because counterfactual hold actions are not observed.

\paragraph{Auxiliary executable rollout.}
Sampled BusSimEnv rollout is reported only as an auxiliary sanity check because only Austin and Halifax have runnable generated line environments.
For this rollout, each policy is evaluated on the same line-level random seed, including Python signal-delay randomness, and live observations are mapped back to the static-transition feature schema before model scoring.
The policy score uses the BusSimEnv linear headway reward rather than the static one-step reward.

\begin{table}[t]
\centering
\small
\resizebox{\textwidth}{!}{\input{../cf_h2o/results/paper_artifacts/tables/experiment_scope_table.tex}}
\caption{Experimental scope and paper role. The primary evidence is strict city-level leave-one-out dynamics and one-step policy validation.}
\label{tab:scope}
\end{table}
