\section{Discussion}

\paragraph{Why factored residuals help.}
The dense residual baseline has enough capacity to fit cross terms in source data, but the same flexibility can mix city-specific demand, speed, and headway effects.
\ours restricts each output to a smaller mechanism-specific parent set.
This constraint appears helpful in the strict cross-city setting: it reduces total MSE on all four targets and makes source weighting more effective.

\paragraph{What the source weighting does and does not show.}
Similarity weighting improves the mean strict leave-one-out ratio from $0.759$ to $0.578$ and wins over unweighted \ours on three of four targets.
The Singapore target is the exception, where weighting is slightly worse than unweighted \ours.
This suggests that static similarity is useful but imperfect; city descriptors built from open data may miss route-level operational differences that matter for transfer.

\paragraph{Policy evidence remains secondary.}
The one-step policy validation and sampled BusSimEnv rollout are useful checks, but they do not replace a closed-loop operational benchmark.
The rollout result reaches reward parity with \Htwo only after aligning BusSimEnv observations to the static feature schema and using identical line-level random seeds across policies.
That correction is necessary for a fair comparison, but the resulting rollout margin is small.
The strongest claim should therefore remain dynamics transfer plus policy-proxy improvement, not full policy dominance.

\paragraph{Static-derived validation is not operational validation.}
The central limitation is target construction.
The experiments use full-route open static data and deterministic transition rules to create paired simulator/target transitions.
This is valuable for reproducibility and reviewer scrutiny, but it is not the same as evaluating counterfactual holding actions on AVL/APC trajectories or a calibrated live SUMO rollout.
The Austin raw APC/AVL slice partially addresses the trajectory-ground-truth concern for passive action-$0$ dynamics, but it still cannot identify how unobserved holding actions would have changed passenger and headway outcomes.
The paper should therefore avoid claims such as ``CFCMT is better on real bus systems''.
A precise claim is: under open static-data-derived cross-city validation with little or no target-city calibration, and under passive real APC validation with few-shot adaptation, mechanism-factored residual transfer is more robust than dense residual correction.

\paragraph{How to strengthen the next version.}
The most valuable addition would be counterfactual or interventional validation on one city with vehicle-level AVL/APC trajectories, even if only for a subset of routes.
The second priority is to expand executable line environments so sampled rollout can move from auxiliary sanity check to a stronger policy benchmark.
The third priority is to add more cities, because city-level generalization is ultimately limited by the number of held-out cities.
